An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-06-02 poly-embed-journal/poly-embed-journal.tex
Starting in Sec 5

@@

\begin{proposition}\label{prop:tfae-min-rep-nonredundant}
  Let $\U$ be a finite representative set for $L$ eliciting $\Gamma$.
  $\U$ is a minimum representative set for $L$ if and only if $L|_{U}$ is non-redundant.
\end{proposition}
\begin{proof}[Sketch]
  $\Rightarrow$  
  We show the contrapositive: suppose $L|_{U}$ is redundant.
  Then there is a $r,r' \in \U$ such that $\Gamma_r \subseteq \Gamma_{r'}$.
  Then for all $p \in \Gamma_r$, we have $\{r, r'\} \subseteq \Gamma(p)$.
  Therefore, $\U \setminus \{r\}$ still a representative set, so $\U$ is not minimum.

@@

  $\Leftarrow$
  \btw{Commented out version relying on hyperplanes without power diagrams; it was incorrect - Jessie 1 June 21}
  Since $\U$ is a finite representative set, we know $L|_\U$ is embedded by $L$ nu Corollary~\ref{cor:representative-embeds-restriction}.
  Therefore, $\Gamma := \prop{L}$ embeds $\Gamma|_\U := \prop{L|_\U}$, and by assumption $\Gamma|_\U$ is non-redundant.
  By Proposition~\ref{prop:embed-trim}\jessiet{BTW: Forward ref}, $\U$ is a minimum representative set for $L$.
%  Since $\R^*$ is finite, it suffices to show that for all $r \in \R^*$, there exists some $p_r \in \simplex$ such that $\{r\} = \Gamma(p_r)$.
%  This implies the result, as removing $r$ from $\R^*$ would make $\Gamma(p_r) = \emptyset$, and therefore $\R^* \setminus \{r\}$ would not be representative.
%  
%  If there was an $r \in \R^*$ such that there was no such $p_r$, but $\Gamma_r \not \subseteq \Gamma_{r'}$ for any other $r' \in \R^*$, then we must have some $r', r''$ such that there exists a $p_{r'}^r$ and $p_{r''}^r$ such that $\{r,r'\} \subseteq \Gamma(p_{r'}^r)$ and $r'' \not \in p_{r'}^r$, and similarly, $\{r, r''\} \subseteq \Gamma(p_{r''}^r)$ and $r' \not \in \Gamma(p_{r''}^r)$.
%  
%  Observe that the hyperplane $H_L(p; u) := p \mapsto \inprod{p}{L(u)}$ supports $\risk{L}$ at $p$ if and only if $r \in \Gamma(p)$.
%  By assumption, we have $H_L(p_{r'}^r; r)$ supporting $\risk{L}(p_{r'}^r)$ and $H_L(p_{r''}^r; r)$ supporting $\risk{L}(p_{r''}^r)$.
%  As $H_L(\cdot;r)$ is linear in its first argument (this is true for any $r \in \R^*$), then $\risk{L}$ must be linear between $p_{r'}^r$ and $p_{r''}^r$.
%  
%  Now observe that 
%  $r' \in \Gamma(p_{r'}^r) \iff H_L(p_{r'}^r; r')$ supports $\risk{L}(p_{r'}^r)$.
%  Since $\risk{L}$ is linear between $p_{r'}^r$ and $p_{r''}^r$, \jessie{THIS IS INCORRECT} it therefore also supports $\risk{L}(p_{r''}^r) \iff r' \in \Gamma(p_{r''}^r)$, yielding a contradiction.
%  
%  Therefore, for all $r \in \R^*$, there must be some $p_r$ such that $\Gamma(p_r) = \{r\}$, and thus $\R^*$ is a minimum representative set.

@@

\begin{corollary}
  If $\R$ is a minimum representative set for $L$, then $L$ tightly embeds $L|_\R$.
\end{corollary}
Tightly embedding the restricted loss seems to make embedding construction slightly easier.
While $L|_\R$ is not always the target loss of interest, there should now be a \emph{bijection} from $\R$ to the target reports.
While an embedding only has to be constructed once and is considered an offline computation, its construction might be made easier

\begin{proposition}\label{prop:trim-unique}
  Suppose $\R$ and $\R'$ are finite minimum representative sets for the loss $L$.
  Then $\{L(r) \mid r \in \R\} = \{L(r') \mid r' \in \R'\}$.
\end{proposition}
\begin{proof}[Sketch]
  It suffices to show $\{L(r) \mid r \in \R\} \subseteq \{L(r') \mid r' \in \R'\}$, and equality will follow by symmetry.
  Consider $r\in \R$, and we want to show $L(r) \in \{L(r') \mid r' \in \R'\}$.
  Since $\R$ and $\R'$ are minimum representative sets, all the level sets must be full-dimensional, and therefore have well-defined interiors (Proposition~\ref{prop:tfae-min-rep-nonredundant}).
  In particular, we must have $\Gamma_r = \Gamma_{r'}$ for some $r' \in \R'$.
  If $L(r) \neq L(r')$, then there would be a distribution $p \in \inter{\Gamma_r}$ such that $\inprod{p}{L(r)} \neq \inprod{p}{L(r')}$. \jessiet{This needs more detail}
  If $\inprod{p}{L(r)} > \inprod{p}{L(r')}$, then $r' \not \in \Gamma(p)$, and $\R'$ is therefore not a representative set.
  Similarly, if the inequality were flipped, we would contradict $\R$ being a representative set.
  Therefore, we must have the losses equal, and $L(r) \in \{L(r') \mid r' \in \R'\}$.
\end{proof}

@@

@@

  Finally, consider that $\trim(L) = \trim(\ell)$ implies $L$ embeds $\ell$, and if $\R^*$ is a minimum representative set for $\ell$ then $\trim(\ell) = \trim(\ell|_{\R^*})$ and $\ell|_{\R^*}$ is non-redundant.
  Therefore, $L$ tightly embeds $\ell|_{\R^*}$.
\end{proof}

As we define one loss embedding another, one can imagine an analogous definition where one property embeds another, and we can define $\trim(\Gamma)$ as the set of level sets generated by a minimum representative set.
Even when using the language of properties, similar results to those above hold; for intuition, the level sets of a property correspond to the subgradients of the Bayes Risk of the loss eliciting it.
Since embedding also means matching Bayes Risks, the $\trim$s matching follows since the subgradients also trivially match.

@@

\begin{restatable}{proposition}{embedtrim}\label{prop:embed-trim}
	Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
	The following are equivalent:
	\begin{enumerate}\setlength{\itemsep}{0pt}
		\item $\Gamma$ embeds a \jessie{nonredundant} finite property $\gamma:\simplex \toto \R$.
		\item $\trim(\Gamma)$ is a finite set, and $\cup\,\trim(\Gamma) = \simplex$.
		\item There is a finite minimum representative set $\U$ for $\Gamma$.
		\item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
	\end{enumerate}
	% \raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
	Moreover, when any of the above hold, $\trim(\gamma) = \trim(\Gamma) = \{\Gamma_u : u\in\U\} = \Theta$, and $\gamma$ is elicitable.
\end{restatable}
\begin{proof}
	Let $L$ elicit $\Gamma$.

@@

	3 $\Rightarrow$ 1:
	Since $\U$ is representative, we have $\Gamma(p) \cap \U$ nonempty for all $p \in \simplex$, and therefore, $\Gamma$ embeds $\Gamma|_\U$, which is finite as $\U$ is finite.
	Since $\U$ is minimum, the constructed $\Gamma_\U$ is additionally non-redundant.

@@

\subsection*{Acknowledgements}
We thank Arpit Agarwal and Peter Bartlett for many early discussions, which led to several important insights.
% to a proof of %\raf{1-d reduction} among other insights.
% Additionally, we thank Arpit Agarwal for early insights and bringing out attention to the abstain property.
We thank Eric Balkanski for help with a lemma about submodular functions. %Lemma~\ref{lem:bar-f}\jessie{We don't have the Lov\'asz hinge appendix here?}.
This material is based upon work supported by the National Science Foundation under Grants No.\ 1657598 and No.\ DGE 1650115.
\raf{Nishant, anyone else now?}
\newpage
\bibliographystyle{plainnat}
\bibliography{diss,extra}

@@

\iffalse
\section{Embedding properties}\label{app:embed-props}

@@

It is often convenient to work directly with properties and set aside the losses which elicit them.
To this end, we say a property to embeds another if eq.~\eqref{eq:embed-loss} holds.
We begin with the notion of redundancy.
\begin{definition}[Finite property, non-redundant]
  A property $\gamma:\simplex\toto\R$ is \emph{redundant} if for some $r,r'\in\R$ with $r \neq r'$, we have $\gamma_r \subseteq \gamma_{r'}$, and \emph{non-redundant} otherwise.
  $\gamma$ is \emph{finite} if it is non-redundant and $\R$ is a finite set.
\end{definition}

@@

\begin{definition}\label{def:trim}
  Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trim(\Gamma) = \{\Gamma_u : u \in \R \text{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$ as the set of maximal level sets of $\Gamma$.
\end{definition}

@@

\hrule
\bigskip
\jessie{Add results (subsection?) relating trim and positive normal sets.  From here until the hrule}
\subsection{Relation to Positive Normal Sets}

@@

When working with convex surrogates which are not strictly convex, one quickly encounters redundant properties: if $\inprod{p}{L(\cdot)}$ is minimized by a point where $\inprod{p}{L}$ is flat, then there will be an uncountable set of reports which also minimize the expected loss.
As results in property elicitation typically assume properties are non-redundant (e.g.~\cite{frongillo2014general,frongillo2015elicitation}), 
% it is useful to consider a transformation which removes redundant level sets, captured by the \emph{trim} operation.

@@

\btw{JESSIE: Figures/an example might help clarify this}
When a property $\Gamma$ embeds a finite property $\gamma$, we can show that the level sets of $\gamma$ correspond exactly to their embedded level sets of $\Gamma$, and that these embedded level sets are exactly $\trim(\Gamma)$.
\jessiet{This lemma new to journal version}
\begin{lemma}\label{lem:embedded-level-sets-trim}
  Let $\Gamma$ be an elicitable property.
  If $\Gamma$ embeds a (non-redundant) finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then $\{\gamma_r : r \in \R\} = \{\Gamma_u : u \in \varphi(\R)\} = \trim(\Gamma)\proposedadd{=\trim(\gamma)}$.
  \proposedadd{RETRY: Let $\Gamma$ be an elicitable property.
    If $\Gamma$ embeds a finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then for any minimum representative set $\Sc$ for $\gamma$, we have $\{\gamma_r : r \in \Sc\} = \{\Gamma_u : u \in \varphi(\Sc)\} = \trim(\Gamma)=\trim(\gamma)$.}
\end{lemma}
\begin{proof}
  Let $L$ elicit $\Gamma$.
  Take $\ell$ to be the loss embedded by $L$ from Lemma~\ref{lem:embed-defs-equiv}.
  Moreover, by Proposition~\ref{prop:embed-bayes-risks}, we have $\risk{L} = \risk{\ell}$.
  % \raft{Implicitly? Justify the claim.  \jessie{In definition of finite properties, we say that we assume we are talking about non-redundant.}}
  As $\gamma$ is finite (and non-redundant by assumption), we know that each level set of $\gamma$ must be full-dimensional in $\affhull(\simplex)$. 
  For all $r \in \R$, we know $\gamma_r = \Gamma_{\varphi(r)}$, so we must also have $\Gamma_{\varphi(r)}$ full-dimensional.
  Moreover, we have $\{\gamma_r : r \in \R\} = \{\Gamma_{\varphi(r)} : r \in \R\}$ as a corollary since this is true for each $r \in \R$.
  \raft{The main action is here.  (1) Epigraph of $-\risk{L}$. (2) There is really only one case: every level set is a face of the power diagram, which must be contained (weakly, so $\subseteq$) in a facet. (3) To show that level sets are faces, you'll want to appeal to some piece of a proof in the prev section.}
  Since the cell $\Gamma_{\varphi(r)}$ is the projection of a facet of the epigraph of $-\risk{L}$, which is convex, any other level set intersecting $\Gamma_{\varphi(r)}$ can be considered as faces of the epigraph of $-\risk{L}$, and therefore a face of the induced power diagram.
  Therefore, we remove lower-dimensional faces, as they are proper subsets of the level sets of embedded reports, and conclude such $\Gamma_u \not \in \trim(\Gamma)$.
  % in one of two cases:
  % First, if the level set $\Gamma_u$ (for $u \not \in \varphi(\R)$) is a projection of a lower-dimensional face of $\risk{L}$, which is contained in a facet of the epigraph.
  % Therefore, we must have $\Gamma_u \subset \Gamma_{\varphi(r)}$ for some $r \in \R$, and therefore $\Gamma_u \not \in \trim(\Gamma)$.

  Second, $\Gamma_u = \Gamma_{\varphi(r)}$ for some $r \in \R$, then the level set is in both $\{\Gamma_{\varphi(r)} : r \in \R\}$ and $\trim(\Gamma)$.

  \proposedadd{First, construct $\Sc := \Sc(L)$ as Definition~\ref{cons:rep-set}\jessiet{Argue there is a bijection from this set to any other minimum representative set}, which is a minimum representative set by Proposition~\ref{prop:SL-minimum}. 
    Moreover, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$ by embedding, and therefore $\gamma_r = \Gamma_{\varphi(r)}$, yielding $\{\gamma_r \mid r \in \Sc\} = \{\Gamma_{\varphi(r)} \mid r \in \Sc\}$ as this is true for all $r \in \Sc$.}

  \proposedadd{Now let $T := \{\gamma_r \mid r \in \Sc\} = \trim(\gamma)$. 
    First, if $\gamma_r \in T$, then it is not a subset of any level set as $\gamma_r$ is full-dimensional in the simplex as it corresponds to a facet of the epigraph of the negative risk $E_\ell$, and the supporting hyperplane is therefore unique.
    Now, if $\theta \in \trim(\gamma)$, then there is some report $r'$ such that $\theta = \gamma_{r'}$.
    If $r' \not \in \Sc$, we want to claim there is some $r$ such that $\gamma_{r'} = \gamma_r$.
    As $\theta$ is a maximal level set, it has a nonempty interior.
    Therefore, for any $p \in \inter{\theta}$ (and one such $p$ must exist), the hyperplane $p \mapsto (p, \ell(r'))$ uniquely supports the epigraph of negative risk.
    If $r' \not \in \Sc$, then there must be some $r \in \Sc$ such that $p \mapsto (p, \ell(r))$ also supports the same facet of $E_\ell$; if no such $r \in \Sc$ existed, we would contradict our claim that $\Sc$ is representative for $\ell$.
    Similarly, we have $\{\Gamma_u \mid u \in \varphi(\Sc)\} = \trim(\Gamma)$ by the same logic.}
\end{proof}

>>>>

This motivates us to think about what it means to embed a non-redundant loss, and consider the implications this has for representative set.

@@

\begin{proposition}\label{prop:tfae-min-rep-nonredundant}
  Let $\U$ be a finite representative set for $L$ eliciting $\Gamma$.
  $\U$ is a minimum representative set for $L$ if and only if $L|_{\U}$ is non-redundant.
\end{proposition}
\begin{proof}
  $\Rightarrow$  
  We show the contrapositive: suppose $L|_{\U}$ is redundant.
  Then there is a $r,r' \in \U$ such that $\Gamma_r \subseteq \Gamma_{r'}$.
  Then for all $p \in \Gamma_r$, we have $\{r, r'\} \subseteq \Gamma(p)$.
  Therefore, $\U \setminus \{r\}$ still a representative set, so $\U$ is not minimum.

@@

  $\Leftarrow$
  \btw{Commented out version relying on hyperplanes without power diagrams; it was incorrect - Jessie 1 June 21}
  Since $\U$ is a finite representative set, we know $L|_\U$ is embedded by $L$ in Corollary~\ref{cor:representative-embeds-restriction}.
  Therefore, $\Gamma := \prop{L}$ embeds $\Gamma|_\U := \prop{L|_\U}$ (see Definition~\ref{def:prop-embed} in \S~\ref{app:embed-props}).
  Since $\Gamma|_\U$ is non-redundant by assumption, we can apply Proposition~\ref{prop:embed-trim}\jessiet{BTW: Forward ref}, $\U$ is a minimum representative set for $L$.
%  Since $\R^*$ is finite, it suffices to show that for all $r \in \R^*$, there exists some $p_r \in \simplex$ such that $\{r\} = \Gamma(p_r)$.
%  This implies the result, as removing $r$ from $\R^*$ would make $\Gamma(p_r) = \emptyset$, and therefore $\R^* \setminus \{r\}$ would not be representative.
%  
%  If there was an $r \in \R^*$ such that there was no such $p_r$, but $\Gamma_r \not \subseteq \Gamma_{r'}$ for any other $r' \in \R^*$, then we must have some $r', r''$ such that there exists a $p_{r'}^r$ and $p_{r''}^r$ such that $\{r,r'\} \subseteq \Gamma(p_{r'}^r)$ and $r'' \not \in p_{r'}^r$, and similarly, $\{r, r''\} \subseteq \Gamma(p_{r''}^r)$ and $r' \not \in \Gamma(p_{r''}^r)$.
%  
%  Observe that the hyperplane $H_L(p; u) := p \mapsto \inprod{p}{L(u)}$ supports $\risk{L}$ at $p$ if and only if $r \in \Gamma(p)$.
%  By assumption, we have $H_L(p_{r'}^r; r)$ supporting $\risk{L}(p_{r'}^r)$ and $H_L(p_{r''}^r; r)$ supporting $\risk{L}(p_{r''}^r)$.
%  As $H_L(\cdot;r)$ is linear in its first argument (this is true for any $r \in \R^*$), then $\risk{L}$ must be linear between $p_{r'}^r$ and $p_{r''}^r$.
%  
%  Now observe that 
%  $r' \in \Gamma(p_{r'}^r) \iff H_L(p_{r'}^r; r')$ supports $\risk{L}(p_{r'}^r)$.
%  Since $\risk{L}$ is linear between $p_{r'}^r$ and $p_{r''}^r$, \jessie{THIS IS INCORRECT} it therefore also supports $\risk{L}(p_{r''}^r) \iff r' \in \Gamma(p_{r''}^r)$, yielding a contradiction.
%  
%  Therefore, for all $r \in \R^*$, there must be some $p_r$ such that $\Gamma(p_r) = \{r\}$, and thus $\R^*$ is a minimum representative set.

@@

\begin{corollary}\label{cor:tight-embed-min-rep}
  If $\R$ is a minimum representative set for $L$, then $L$ tightly embeds $L|_\R$.
\end{corollary}
Tightly embedding the restricted loss seems to make embedding construction slightly easier.
While $L|_\R$ is not always the target loss of interest, there should now be a \emph{bijection} from $\R$ to the target reports.
While an embedding only has to be constructed once and is considered an offline computation, its construction might be made easier by a tight embedding.

We now present a concept called the $\trim$ of a loss (see Definition~\ref{def:trim-prop} for an analogous definition for properties in \S~\ref{app:embed-props}) which lets us focus on a unique set of loss vectors (resp., property values) induced by any minimum representative set.

\begin{proposition}\label{prop:trim-unique}
  Suppose $\R$ and $\R'$ are finite minimum representative sets for the loss $L$.
  Then $\{L(r) \mid r \in \R\} = \{L(r') \mid r' \in \R'\}$.
\end{proposition}
\begin{proof}
  It suffices to show $\{L(r) \mid r \in \R\} \subseteq \{L(r') \mid r' \in \R'\}$, and equality will follow by symmetry.
  Consider $r\in \R$, and we want to show $L(r) \in \{L(r') \mid r' \in \R'\}$.
  Since $\R$ and $\R'$ are minimum representative sets, all the level sets must be full-dimensional, and therefore have well-defined interiors (Proposition~\ref{prop:tfae-min-rep-nonredundant}).
  In particular, we must have $\Gamma_r = \Gamma_{r'}$ for some $r' \in \R'$.
  If $L(r) \neq L(r')$, then there would be a distribution $p \in \inter{\Gamma_r}$ such that $\inprod{p}{L(r)} \neq \inprod{p}{L(r')}$. \jessiet{This needs more detail}
  If $\inprod{p}{L(r)} > \inprod{p}{L(r')}$, then $r' \not \in \Gamma(p)$, and $\R'$ is therefore either not a representative set or not minimum.
  Similarly, if the inequality were flipped, we would contradict either $\R$ being a representative set or minimum.
  Therefore, we must have the losses equal, and $L(r) \in \{L(r') \mid r' \in \R'\}$.
\end{proof}

@@

It turns out that the $\trim$ of two losses being equal is equivalent to embedding, and additionally implies the existence of a tight embedding for a loss restricted to any minimum representative set.

@@

  Finally, consider that $\trim(L) = \trim(\ell)$ implies $L$ embeds $\ell$, and if $\R^*$ is a minimum representative set for $\ell$ then $\trim(L) = \trim(\ell) = \trim(\ell|_{\R^*})$ so $L$ tightly embeds $\ell|_{\R^*}$ by Corollary~\ref{cor:tight-embed-min-rep} and composing the embeddings.
  % and $\ell|_{\R^*}$ is non-redundant by Proposition~\ref{prop:tfae-min-rep-nonredundant}.
  Therefore, $L$ tightly embeds $\ell|_{\R^*}$.
\end{proof}

As we define one loss embedding another, one can imagine an analogous definition where one property embeds another (Definition~\ref{def:prop-embed}), and we can define $\trim(\Gamma)$ as the set of level sets generated by a minimum representative set (Definition~\ref{def:trim-prop}).
See \S~\ref{app:embed-props} for precise definitions and discussion.
Even when using the language of properties, similar results to those above hold; for intuition, the level sets of a property correspond to the subgradients of the Bayes risk of the loss eliciting it.
Since embedding also means matching Bayes risks, the $\trim$s matching follows since the subgradients also trivially match.

@@

\begin{restatable}{proposition}{embedtrim}\label{prop:embed-trim}
	Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
	The following are equivalent:
	\begin{enumerate}\setlength{\itemsep}{0pt}
		\item $\Gamma$ embeds a \jessie{non-redundant} finite property $\gamma:\simplex \toto \R$.
		\item $\trim(\Gamma)$ is a finite set, and $\cup\,\trim(\Gamma) = \simplex$.
		\item There is a finite minimum representative set $\U$ for $\Gamma$.
		\item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
	\end{enumerate}
	% \raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
	Moreover, when any of the above hold, $\trim(\gamma) = \trim(\Gamma) = \{\Gamma_u : u\in\U\} = \Theta$, and $\gamma$ is elicitable.
\end{restatable}
\begin{proof}
	Let $L$ elicit $\Gamma$.

@@

	3 $\Rightarrow$ 1:
	Since $\U$ is representative, we have $\Gamma(p) \cap \U$ nonempty for all $p \in \simplex$, and therefore, $\Gamma$ embeds $\Gamma|_\U$, which is finite as $\U$ is finite.
	Since $\U$ is minimum, the constructed $\Gamma_\U$ is additionally non-redundant.
	\jessiet{Want more details here.  It's the forward implication of Prop 4, but since this is used in the reverse implication of prop 4, don't want to create cyclic dependencies.}

@@

\subsection*{Acknowledgements}
We thank Arpit Agarwal and Peter Bartlett for many early discussions, which led to several important insights.
% to a proof of %\raf{1-d reduction} among other insights.
% Additionally, we thank Arpit Agarwal for early insights and bringing out attention to the abstain property.
We thank Eric Balkanski for help with a lemma about submodular functions. %Lemma~\ref{lem:bar-f}\jessie{We don't have the Lov\'asz hinge appendix here?}.
This material is based upon work supported by the National Science Foundation under Grants No.\ 1657598 and No.\ DGE 1650115.
\raf{Nishant, anyone else now?}\jessie{Stephen}
\newpage
\bibliographystyle{plainnat}
\bibliography{diss,extra}

@@

\section{Embedding properties}\label{app:embed-props}

@@

%It is often convenient to work directly with properties and set aside the losses which elicit them.
%To this end, we say a property to embeds another if eq.~\eqref{eq:embed-loss} holds.
%We begin with the notion of redundancy.
%\begin{definition}[Finite property, non-redundant]
%  A property $\gamma:\simplex\toto\R$ is \emph{redundant} if for some $r,r'\in\R$ with $r \neq r'$, we have $\gamma_r \subseteq \gamma_{r'}$, and \emph{non-redundant} otherwise.
%  $\gamma$ is \emph{finite} if it is non-redundant and $\R$ is a finite set.
%\end{definition}

@@

\begin{definition}\label{def:trim-prop}
  Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trim(\Gamma) = \{\Gamma_u : u \in \U \}$ as the set of maximal level sets of $\Gamma$ for any minimum representative set $\U \subseteq \R$.
\end{definition}

@@

\iffalse
\hrule
\bigskip
\jessie{Add results (subsection?) relating trim and positive normal sets.  From here until the hrule}
\subsection{Relation to Positive Normal Sets}

@@

\jessiet{GO THROUGH THIS}
When working with convex surrogates which are not strictly convex, one quickly encounters redundant properties: if $\inprod{p}{L(\cdot)}$ is minimized by a point where $\inprod{p}{L}$ is flat, then there will be an uncountable set of reports which also minimize the expected loss.
As results in property elicitation typically assume properties are non-redundant (e.g.~\cite{frongillo2014general,frongillo2015elicitation}), 
% it is useful to consider a transformation which removes redundant level sets, captured by the \emph{trim} operation.

@@

\btw{Commented out result about old trim def = new trim def - Jessie 2 June 21}
%\btw{JESSIE: Figures/an example might help clarify this}
%When a property $\Gamma$ embeds a finite property $\gamma$, we can show that the level sets of $\gamma$ correspond exactly to their embedded level sets of $\Gamma$, and that these embedded level sets are exactly $\trim(\Gamma)$.
%\jessiet{This lemma new to journal version}
%\begin{lemma}\label{lem:embedded-level-sets-trim}
%  Let $\Gamma$ be an elicitable property.
%  If $\Gamma$ embeds a (non-redundant) finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then $\{\gamma_r : r \in \R\} = \{\Gamma_u : u \in \varphi(\R)\} = \trim(\Gamma)\proposedadd{=\trim(\gamma)}$.
%  \proposedadd{RETRY: Let $\Gamma$ be an elicitable property.
%    If $\Gamma$ embeds a finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then for any minimum representative set $\Sc$ for $\gamma$, we have $\{\gamma_r : r \in \Sc\} = \{\Gamma_u : u \in \varphi(\Sc)\} = \trim(\Gamma)=\trim(\gamma)$.}
%\end{lemma}
%\begin{proof}
%  Let $L$ elicit $\Gamma$.
%  Take $\ell$ to be the loss embedded by $L$ from Lemma~\ref{lem:embed-defs-equiv}.
%  Moreover, by Proposition~\ref{prop:embed-bayes-risks}, we have $\risk{L} = \risk{\ell}$.
%  % \raft{Implicitly? Justify the claim.  \jessie{In definition of finite properties, we say that we assume we are talking about non-redundant.}}
%  As $\gamma$ is finite (and non-redundant by assumption), we know that each level set of $\gamma$ must be full-dimensional in $\affhull(\simplex)$. 
%  For all $r \in \R$, we know $\gamma_r = \Gamma_{\varphi(r)}$, so we must also have $\Gamma_{\varphi(r)}$ full-dimensional.
%  Moreover, we have $\{\gamma_r : r \in \R\} = \{\Gamma_{\varphi(r)} : r \in \R\}$ as a corollary since this is true for each $r \in \R$.
%  \raft{The main action is here.  (1) Epigraph of $-\risk{L}$. (2) There is really only one case: every level set is a face of the power diagram, which must be contained (weakly, so $\subseteq$) in a facet. (3) To show that level sets are faces, you'll want to appeal to some piece of a proof in the prev section.}
%  Since the cell $\Gamma_{\varphi(r)}$ is the projection of a facet of the epigraph of $-\risk{L}$, which is convex, any other level set intersecting $\Gamma_{\varphi(r)}$ can be considered as faces of the epigraph of $-\risk{L}$, and therefore a face of the induced power diagram.
%  Therefore, we remove lower-dimensional faces, as they are proper subsets of the level sets of embedded reports, and conclude such $\Gamma_u \not \in \trim(\Gamma)$.
%  % in one of two cases:
%  % First, if the level set $\Gamma_u$ (for $u \not \in \varphi(\R)$) is a projection of a lower-dimensional face of $\risk{L}$, which is contained in a facet of the epigraph.
%  % Therefore, we must have $\Gamma_u \subset \Gamma_{\varphi(r)}$ for some $r \in \R$, and therefore $\Gamma_u \not \in \trim(\Gamma)$.
%  Second, $\Gamma_u = \Gamma_{\varphi(r)}$ for some $r \in \R$, then the level set is in both $\{\Gamma_{\varphi(r)} : r \in \R\}$ and $\trim(\Gamma)$.
%  \proposedadd{First, construct $\Sc := \Sc(L)$ as Definition~\ref{cons:rep-set}\jessiet{Argue there is a bijection from this set to any other minimum representative set}, which is a minimum representative set by Proposition~\ref{prop:SL-minimum}. 
%    Moreover, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$ by embedding, and therefore $\gamma_r = \Gamma_{\varphi(r)}$, yielding $\{\gamma_r \mid r \in \Sc\} = \{\Gamma_{\varphi(r)} \mid r \in \Sc\}$ as this is true for all $r \in \Sc$.}
%  \proposedadd{Now let $T := \{\gamma_r \mid r \in \Sc\} = \trim(\gamma)$. 
%    First, if $\gamma_r \in T$, then it is not a subset of any level set as $\gamma_r$ is full-dimensional in the simplex as it corresponds to a facet of the epigraph of the negative risk $E_\ell$, and the supporting hyperplane is therefore unique.
%    Now, if $\theta \in \trim(\gamma)$, then there is some report $r'$ such that $\theta = \gamma_{r'}$.
%    If $r' \not \in \Sc$, we want to claim there is some $r$ such that $\gamma_{r'} = \gamma_r$.
%    As $\theta$ is a maximal level set, it has a nonempty interior.
%    Therefore, for any $p \in \inter{\theta}$ (and one such $p$ must exist), the hyperplane $p \mapsto (p, \ell(r'))$ uniquely supports the epigraph of negative risk.
%    If $r' \not \in \Sc$, then there must be some $r \in \Sc$ such that $p \mapsto (p, \ell(r))$ also supports the same facet of $E_\ell$; if no such $r \in \Sc$ existed, we would contradict our claim that $\Sc$ is representative for $\ell$.
%    Similarly, we have $\{\Gamma_u \mid u \in \varphi(\Sc)\} = \trim(\Gamma)$ by the same logic.}

%\jessiet{03.01.21 - Old version of Prop~\ref{prop:embed-trim} moved to comment}
% \jessiet{Can we remove this?}
% \begin{proof}[Original]
%   Let $L$ elicit $\Gamma$.
%   
%   1 $\Rightarrow$ 2:
%   By the embedding condition, taking $\R_1 = \reals^d$ and $\R_2 = \varphi(\R)$ satisfies the conditions of Lemma~\ref{lem:loss-restrict}: for all $p\in\simplex$, as $\gamma(p) \neq \emptyset$ by definition, we have some $r\in\gamma(p)$ and thus some $\varphi(r) \in \Gamma(p)$.
%   Let $G(p) := -\min_{u\in\reals^d} \inprod{p}{L(u)}$ be the negative Bayes risk of $L$, which is convex, and $G_{\R}$ that of $L|_{\varphi(\R)}$.
%   By the Lemma, we also have $G = G_\R$.
%   As $\gamma$ is finite, $G$ is polyhedral.
%   Moreover, the projection of the epigraph of $G$ onto $\simplex$ forms a power diagram, with the facets projecting onto the level sets of $\gamma$, the cells of the power diagram.
%   (See Theorem~\ref{thm:aurenhammer}.)
%   As $L$ elicits $\Gamma$, for all $u\in\reals^d$, the hyperplane $p\mapsto \inprod{p}{L(u)}$ is a supporting hyperplane of the epigraph of $G$ at $(p,G(p))$ if and only if $u\in\Gamma(p)$.
%   This supporting hyperplane exposes some face $F$ of the epigraph of $G$, which must be contained in some facet $F'$.
%   Thus, the projection of $F$, which is $\Gamma_u$, must be contained in the projection of $F'$, which is a level set of $\gamma$.
%   We conclude that $\Gamma_u \subseteq \gamma_r$ for some $r\in\R$.
%   Hence, $\trim(\Gamma) = \{\gamma_r : r\in\R\}$, which is finite, and unions to $\simplex$.
%   
%   2 $\Rightarrow$ 3: let $\R = \{u_1,\ldots,u_k\} \subseteq\reals^d$ be a set of distinct reports such that $\trim(\Gamma) = \{\Gamma_{u_1},\ldots,\Gamma_{u_k}\}$.
%   Now as $\cup\,\trim(\Gamma) = \simplex$, for any $p\in\simplex$, we have $p\in\Gamma_{u_i}$ for some $u_i\in\R$, and thus $\Gamma(p) \cap \R \neq \emptyset$.
%   We now satisfy the conditions of Lemma~\ref{lem:loss-restrict} with $\R_1 = \reals^d$ and $\R_2 = \R$.
%   The property $\gamma:p\mapsto\Gamma(p)\cap\R$ is non-redundant by the definition of $\trim$, finite, and elicitable.
%   Now from Lemma~\ref{lem:finite-full-dim}, the level sets $\Theta = \{\gamma_r:r\in\R\}$ are full-dimensional, and union to $\simplex$.
%   Statement 3 then follows from the fact that $\gamma_r = \Gamma_r$ for all $r\in\R$.
%   
%   3 $\Rightarrow$ 1: let $\Theta = \{\theta_1,\ldots,\theta_k\}$.
%   For all $i\in\{1,\ldots,k\}$ let $u_i\in\reals^d$ such that $\Gamma_{u_i} = \theta_i$.
%   Now define $\gamma:\simplex\toto\{1,\ldots,k\}$ by $\gamma(p) = \{i : p\in\theta_i\}$, which is non-degenerate as $\cup\,\Theta = \simplex$.
%   By construction, we have $\gamma_i = \theta_i = \Gamma_{u_i}$ for all $i$, so letting $\varphi(i) = u_i$ we satisfy the definition of embedding, namely statement 1.
% \end{proof}
